\LARGE \bf ``Those who can't do teach'': Learning Handwriting by Teaching a Robot

### 2014-08-22 main.tex
Re-enabled + rewritten Future Work section

\section{A Tool for Social and Pedagogical Investigations} \label{sec:experiment}

@@

@@

The work presented opens up the research area of the role for robots in the
education of handwriting and other embodied activities, and makes significant,
novel steps towards addressing the over-arching research question of how
interacting with such a robotic learning partner may be beneficial for
sustaining a child's interaction in handwriting interventions and the impact on
the participating child's motivation, self-esteem, and educational future.

%\subsection{Future Works}
%\section{Future work}

%A number of research questions remain open for investigation in the wider scope
%of the CoWriter project, in addition to those which have been raised as a
%result of the work carried out to develop the presented system.

%In the scope of open technical questions, it remains to be seen how shape
%models for letters might be generated which capture the full range of mistakes
%typical of children learning handwriting: extending the current system capable
%of incorporating internal proportion and global deformation errors to one which
%can also generate missing subparts of the letter, or break the letter down into
%primitive strokes at will, for example. Could incorporating a database of
%letters drawn by children into the shape modeling process facilitate this?

%In terms of the interaction experience, it may be interesting to investigate
%which other technology could be incorporated into the system for a more fluid
%interaction, such as integrating the user's gaze information to infer when the
%user is finished with a demonstration, or using a classification algorithm to
%determine which letter has been demonstrated irrespective of its positioning.

%On the educational side, open questions include how the handwriting error
%generation of the system may be abstracted to a higher level of control so that
%a teacher may configure it to work with a child on a particular type of
%mistakes, based on the child's performance. Where would the balance lie between
%developing autonomous capabilities for the system to determine the child's
%difficulties, and empowering the teaching staff to decide for themselves
%instead? And, as a result, the ultimate question for this area of research is
%to address what impact to the outcomes of a handwriting intervention the
%addition of such a teachable robotic agent would have: does it impact the
%motivation of the participants, their self-esteem, and/or the learning gains
%that they experience?

>>>>

\section{A Tool for Social and Pedagogical Investigations} \label{sec:experiment}
\label{sec4}

@@

\paragraph{Role of the experimenter}

@@

\subsection{Why a robot?}

\subsection{Future Work}

In the scope of open technical questions, it remains to be seen how shape models
for letters might be generated which capture the full range of mistakes typical
of children learning handwriting: extending the current system capable of
incorporating internal proportion and global deformation errors to one which can
also generate missing subparts of the letter, or break the letter down into
primitive strokes at will, for example. While we expect that incorporating a
database of letters drawn by children into the shape modeling process would
facilitate this, the current system has conceptual (a PCA only approach can not
generate or learn a different shape topology) and technical (no support for
multi-stroke shapes) limitations that need to be overcome.

In terms of the interaction experience, the current experimental setting, while
technically autonomous, can not robustly recover from situations outside of the
nominal protocol (presented in section~\ref{sec4}), and consequently still requires the
presence of an experimenter. The robot state machine would require to be
extended in non-trivial ways to allow for long, fully autonomous, interactions
with children.

%it may be interesting to investigate
%which other technology could be incorporated into the system for a more fluid
%interaction, such as integrating the user's gaze information to infer when the
%user is finished with a demonstration, or using a classification algorithm to
%determine which letter has been demonstrated irrespective of its positioning.

On the educational side, open questions include how the handwriting error
generation of the system may be abstracted to a higher level of control so that
a teacher may configure it to work with a child on a particular type of
mistakes, based on the child's performance. Where would the balance lie between
developing autonomous capabilities for the system to determine the child's
difficulties, and empowering the teaching staff to decide for themselves
instead? And, as a result, the ultimate question for this area of research is
to address what impact to the outcomes of a long-term handwriting intervention the
addition of such a teachable robotic agent would have: does it impact the
motivation of the participants, their self-esteem, and/or the learning gains
that they experience? We are currently considering running a long-term study
(about 20 hours of interactions per child) that would provide better evidences
to answer these questions.
